Supplementary Material: District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa

### 2023-08-17 paper/supp_figs.tex
Updates from Overleaf

% \begin{landscape}
{\linespread{1}
\small
\begin{longtable}[c]{ll ccc ccc ccc ccc}
      %%%%%%%%%%%%%%%%%%%%
      %%% Table header %%%
      %%%%%%%%%%%%%%%%%%%%
      % Upper layer of table header
      \hline
      % Lines inside the header
      \multicolumn{1}{l}{} & &  &  & \multicolumn{2}{c}{\bf Circumcision Type} \\ 
      \cmidrule(lr){5-7}
       & & {\bf Circumcision} & {\bf Age at} & {\bf Who performed} & {\bf Where was the}  \\
       & & {\bf Status} & {\bf Circumcision} & {\bf the circumcision?} & {\bf circumcision performed?} \\[5pt]
      % Lower lines
      \hline
      \vspace{-5pt}
      \endhead
      %%%%%%%%%%%%%%%%%%%%
      %%% Table footer %%%
      %%%%%%%%%%%%%%%%%%%%
      \\[-5pt]\hline
      \caption{Table of circumcision-related questions included in each survey for each sub-Saharan African country. Surveys which did not include a "Circumcision Status" and "Age at Circumcision" question could not be used, while circumcision type could not be inferred from surveys which did not have a "Who performed the circumcision" and/or "Where was the circumcision performed" question.}
      \endfoot

@@

& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 

@@

& 2017 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 

@@

& 2013 (BAIS) & \checkmark & \xmark & \xmark & \checkmark \\[5pt] 

@@

& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 

@@

& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 

@@

& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 

@@

& 2018 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 

@@

& 2019 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 

@@

& 2007 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[5pt] 

@@

& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 

@@

& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 

@@

& 2017 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 

@@

& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[5pt] 

@@

& 2018 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 

@@

& 2013 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[5pt] 

@@

& 2015 (AIS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 

@@

& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[5pt] 

@@

& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 

@@

& 2019 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 

@@

& 2017 (HSRC) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 

@@

& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt] 

@@

& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[5pt] 

@@

& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[5pt]

\end{longtable}
}

@@

{\linespread{1}
\small
\begin{table}[htbp]
	\centering
	\caption{Criteria used to classify circumcisions from the survey data as MMC or TMC.}
	\label{tab::MCclassification}
	\begin{tabular}{c l | c c c}
	\multirow{2}{*}{} & & \multicolumn{3}{c}{\bf Who performed the circumcision?} \\
	                    &      & \begin{tabular}{c}\bf Healthcare\\[-5pt] \bf Professional\end{tabular} & \begin{tabular}{c}\bf Traditional \\[-5pt] \bf Practioner\end{tabular} & \begin{tabular}{c}\bf Missing\end{tabular} \\
	                          \hline
		% \multirow{3}{*}{\rotatebox{90}{Where performed?}}  & \begin{tabular}{l}Healthcare Facility\end{tabular} & MMC & MMC & MMC \\
		\multirow{3}{*}{\rotatebox{90}{\begin{tabular}{c}\bf Where was it\\[-5pt] \bf performed?\end{tabular}}}  & \begin{tabular}{l}\bf Healthcare\\[-5pt] \bf Facility \end{tabular} & MMC & MMC & MMC \\
		& \begin{tabular}{l}\bf Home, School \\[-5pt] \bf or Ritual Site \end{tabular} & MMC & TMC & TMC \\
		& \begin{tabular}{l} \bf Missing\end{tabular} & MMC & TMC & MC \\
	\end{tabular}	
\end{table}
}

>>>>

% \begin{landscape}
{\linespread{1}
  \footnotesize 
\begin{longtable}[c]{ll ccc c}
      %%%%%%%%%%%%%%%%%%%%
      %%% Table header %%%
      %%%%%%%%%%%%%%%%%%%%
      % Upper layer of table header
      \hline
      % Lines inside the header
      \multicolumn{1}{l}{} & &  &  & \multicolumn{2}{c}{\bf Circumcision Type} \\ 
      \cmidrule(lr){5-6}
       & & {\bf Circumcision} & {\bf Age at} & {\bf Who performed} & {\bf Where was the}  \\
       & & {\bf Status} & {\bf Circumcision} & {\bf the circumcision?} & {\bf circumcision performed?} \\[5pt]
      % Lower lines
      \hline
      \vspace{-3pt}
      \endhead
      %%%%%%%%%%%%%%%%%%%%
      %%% Table footer %%%
      %%%%%%%%%%%%%%%%%%%%
      \\[-3pt] \hline
      \caption{Table of circumcision-related questions included in each survey for each sub-Saharan African country. Surveys which did not include a "Circumcision Status" and "Age at Circumcision" question could not be used, while circumcision type could not be inferred from surveys which did not have a "Who performed the circumcision" and/or "Where was the circumcision performed" question.}
      \endfoot

@@

& 2015 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 

@@

& 2017 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 

@@

& 2013 (BAIS) & \checkmark & \xmark & \xmark & \checkmark \\[3pt] 

@@

& 2010 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 

@@

& 2016 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 

@@

& 2018 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 

@@

& 2018 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 

@@

& 2019 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 

@@

& 2007 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[3pt] 

@@

& 2017 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 

@@

& 2012 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 

@@

& 2017 (MICS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 

@@

& 2005 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[3pt] 

@@

& 2018 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 

@@

& 2013 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[3pt] 

@@

& 2015 (AIS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 

@@

& 2006 (DHS) & \checkmark & \xmark & \xmark & \xmark \\[3pt] 

@@

& 2011 (DHS) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 

@@

& 2019 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 

@@

& 2017 (HSRC) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 

@@

& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark \\[3pt] 

@@

& 2013 (DHS) & \checkmark & \checkmark & \checkmark & \checkmark \\[3pt] 

@@

& 2016 (PHIA) & \checkmark & \checkmark & \checkmark & \xmark 
\end{longtable}
}

@@

{\linespread{1}
\begin{table}[htbp]
	\centering
    \footnotesize
	\caption{Criteria used to classify circumcisions from the survey data as MMC or TMC.}
	\label{tab::MCclassification}
	\begin{tabular}{c l | c c c}
	\multirow{2}{*}{} & & \multicolumn{3}{c}{\bf Who performed the circumcision?} \\
	                    &      & \begin{tabular}{c}\bf Healthcare\\[-5pt] \bf Professional\end{tabular} & \begin{tabular}{c}\bf Traditional \\[-5pt] \bf Practioner\end{tabular} & \begin{tabular}{c}\bf Missing\end{tabular} \\
	                          \hline
		% \multirow{3}{*}{\rotatebox{90}{Where performed?}}  & \begin{tabular}{l}Healthcare Facility\end{tabular} & MMC & MMC & MMC \\
		\multirow{3}{*}{\rotatebox{90}{\begin{tabular}{c}\bf Where was it\\[-5pt] \bf performed?\end{tabular}}}  & \begin{tabular}{l}\bf Healthcare\\[-5pt] \bf Facility \end{tabular} & MMC & MMC & MMC \\
		& \begin{tabular}{l}\bf Home, School \\[-5pt] \bf or Ritual Site \end{tabular} & MMC & TMC & TMC \\
		& \begin{tabular}{l} \bf Missing\end{tabular} & MMC & TMC & MC \\
	\end{tabular}	
\end{table}
}
